Theories of deliberated choice

### 2023-10-27 simple.tex
Rm attempt with border (failed)

\begin{remark}
  Consider a set $S \wsub \Theta$.
  We can define its border as follows.
  Define a converging sequence in $\Theta$ as a sequence of strictly embedded elements $\Theta$, meaning increasing per strict inclusion (so $\theta_1 \ssub \theta_2 \ssub \theta_3…$), and which include every elements of $\hist × I$ (thus $\cup_i(\theta_i)^{-1}(P) = \hist × I$).
  Such a sequence can be associated to a relation ${\allleadstog} \in \allleadstos$ in the natural way (${\allleadstog} = \cup_i(\theta_i)$).
  Define $s_S$ as the set of such sequences.
  The border of $S$ is the set $\set{\cup_i(\theta_i) \suchthat (\theta_i) \in s_S}$.
  Nope, that’s not useful. That border is empty as soon as $\card{\allargs} ≥ 2$.
\end{remark}
\begin{conjecture}
  Each element of $C$ is a forest (here, meaning, an association of each $i$ to a tree, whose nodes are all the triples in the element and related by “the pair in $\allhists × I$ is a close suffix of the pair in the parent”).
  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
\end{conjecture}
\begin{proof}

>>>>

\begin{conjecture}
  Each element of $C$ is a forest (here, meaning, an association of each $i$ to a tree, whose nodes are all the triples in the element and related by “the pair in $\allhists × I$ is a close suffix of the pair in the parent”).
  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
\end{conjecture}
\begin{proof}
